---
title: "Loan_Prediction_markdown"
author: "Gokhul MG"
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(corrplot)
library(psych)
library(VIM)
library(caret)
library(rpart.plot)
library(ROCR)
```

#Read & checkout the Data
```{r}
loandata<-read.csv(file.choose(),header=T,na.strings=c(""," ","NA"))
attach(loandata)
str(loandata)
```

```{r}
loandata$Credit_History <- as.factor(loandata$Credit_History)
summary(loandata)
nrow(loandata)
```

#Check for missing values
```{r}
table(is.na(loandata))
```

#Identify columns having missing values
```{r}
names(which(sapply(loandata, function(x) any(is.na(x)))))
```

#LoanAmount & CreditHistory are important variables.
#Checking how many missing values are in these columns
```{r}
sum(ifelse(is.na(loandata$LoanAmount)==T,1,0))
sum(ifelse(is.na(loandata$Credit_History)==T,1,0))
```

#Identify pattern of data in those Amount & Term
```{r}
unique(LoanAmount)
unique(Loan_Amount_Term)
```

#Tried Building Model with missing values removed.
```{r}
loanDS<- na.omit(loandata)
nrow(loanDS)
```

#Also Tried building model with missing values imputed.
#Both had same accuracy.
```{r}
#All NAs imputed using kNN
#loanDS<- kNN(loandata,k=6)
#table(is.na(loanDS))
```

```{r}
dim(loandata)
dim(loanDS)
names(loanDS)
```

#Remove extra columns added during imputation
```{r}
#loanDS<- loanDS[,c(1:13)]
#summary(loanDS)
```
#Just doing a BoxPlot of LoanAmount
```{r}
boxplot(loanDS$LoanAmount)
boxplot.stats(loanDS$LoanAmount)
```

#Plot Data Distribution Before and After Imputation
```{r}
par(mfrow=c(4,2))

LA1 <- hist(loandata$LoanAmount,col="blue",main="")
LA2 <- hist(loanDS$LoanAmount,col="green",main="")

LT1 <- hist(loandata$Loan_Amount_Term,col="blue",main="")
LT2 <- hist(loanDS$Loan_Amount_Term,col="green",main="")

mtext("Histogram Before & After imputation", side = 3, line = -2, outer = TRUE)
```

#Checking out correlation between numeric variables.
```{r}
cordata=loanDS[c(7,8,9,10)]
corrx <- cor(cordata)
corrplot(corrx ,type = "lower")
```

#Split Train & Validation sets
```{r}
index=sample(1:nrow(loanDS),size=0.7*nrow(loanDS))
loan.train=loanDS[index,]
loan.test=loanDS[-index,]

dim(loan.train)
dim(loan.test)
names(loan.train)
```

#Build a logistic Regression Model using all the independent variables
```{r}
glm_model <- glm(Loan_Status ~ Gender + Married + Dependents + Education + Self_Employed + ApplicantIncome + CoapplicantIncome + LoanAmount + Loan_Amount_Term + Credit_History + Property_Area,
            data = loan.train, family = binomial)

summary(glm_model)
```

```{r}
varImp(glm_model,scale=F)
chisq.test(loan.train$Loan_Status,loan.train$Gender)
```
#Prediction
```{r}
glm_prediction<-predict(glm_model,loan.test[,c(-1,-13)],type="response")
loan.test$prediction=ifelse(glm_prediction>0.5,"Y","N")
loan.test$isTrue<- ifelse((loan.test$Loan_Status==loan.test$prediction),1,0)
accuracy=(sum(loan.test$isTrue==1)/nrow(loan.test))
accuracy
```
#Remove Gender variable and build a model
```{r}
glm_model <- glm(Loan_Status ~ Married + Dependents + Education + Self_Employed + ApplicantIncome + CoapplicantIncome + LoanAmount + Loan_Amount_Term + Credit_History + Property_Area,
                 data = loan.train, family = binomial)

summary(glm_model)
```
#Prediction
```{r}
glm_prediction<-predict(glm_model,loan.test[,c(-1,-13)],type="response")
loan.test$prediction=ifelse(glm_prediction>0.5,"Y","N")
loan.test$isTrue<- ifelse((loan.test$Loan_Status==loan.test$prediction),1,0)
accuracy=(sum(loan.test$isTrue==1)/nrow(loan.test))
accuracy
```

```{r}
confusionMatrix(loan.test$prediction,loan.test$Loan_Status)
```
